Pathogen Spillover - dissertation chapter

### 2016-08-15 pathogen-spillover-diss-ch.Rmd
Revise output.

```{r tables of path coefficients, echo=F}
kable(raw_coefficients,
      caption = "Raw path coefficients")
kable(scaled_coefficients,
      caption = "Standardized path coefficients")
```

@@

## Temperature Figures
```{r temperature figures}
library(ggplot2)
library(scales)
temperatures <- left_join(
      select(summer_temps, plotid, sample_year, hrs_abv25ds),
      select(wet_hrs, plotid, sample_year, hrs1422_wet),
      by = c("plotid","sample_year"))
oak_sod$year <- as.Date(oak_sod$sample_year)

@@

## Rainfall Figures
```{r rainfall figures}
summary(rainy_season_ppt)
```

>>>>

```{r tables of path coefficients, echo=F}
library(knitr)
kable(raw_coefficients,
      caption = "Raw path coefficients")
kable(scaled_coefficients,
      caption = "Standardized path coefficients")
```

@@

## Temperature Figures
```{r temperature figures, echo=F}
library(ggplot2)
library(scales)
temperatures <- left_join(
      select(summer_temps, plotid, sample_year, hrs_abv25ds),
      select(wet_hrs, plotid, sample_year, hrs1422_wet),
      by = c("plotid","sample_year"))
# oak_sod$year <- as.Date(oak_sod$sample_year)

@@

## Rainfall Figures
```{r rainfall figures}
# summary(rainy_season_ppt)
```
